Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-06-14 paper.tex
add data reference

\add{The results for this article were obtained using \texttt{pyJac v2.x.x}.
The most recent version of \texttt{pyJac} can be found at its GitHub repository:
\url{https://github.com/SLACKHA/pyJac}.
All figures, and the data and plotting scripts necessary to reproduce them,
are available openly under the CC-BY license.}\todo{add citations for software and figures etc.\ archive}

>>>>

\add{The results for this article were obtained using \texttt{pyJac v2.x.x}.
The most recent version of \texttt{pyJac} can be found at its GitHub repository:
\url{https://github.com/SLACKHA/pyJac}.
All figures, and the data~\cite{data} and plotting scripts necessary to reproduce them,
are available openly under the CC-BY license.}\todo{add citations for software and figures etc.\ archive}
